---
title: "Wellbeing EDA"
author: "Jason Lu"
date: "2024-01-14"
output: html_document
---


First of all, we visualse WHO-5. This section involves variables who5_21a	who5_21b	who5_21c	who5_21d	who5_21e 
```{r}
WHO5_plot <- function(v, column_name, title) {
  ggplot(mental_wellbeing_data, aes(x=factor(mental_wellbeing_data[[column_name]], 
                            levels = 1:6, 
                            labels = c("All the time", "Most of the time", "More than half of the time",
                                       "Less than half of the time", "Some of the time", "At no time")))) +
    geom_bar(fill="steelblue") +
    labs(title=title, x="", y="Count") +  # Removed x-axis label as the labels are self-explanatory
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 46, hjust = 1))
}

p1_WHO5 <- WHO5_plot(mental_wellbeing_data, "who5_21a", "I have felt cheerful and in good spirits")
p2_WHO5 <- WHO5_plot(mental_wellbeing_data, "who5_21b", "I have felt calm and relaxed")
p3_WHO5 <- WHO5_plot(mental_wellbeing_data, "who5_21c", "I have felt active and vigorous")
p4_WHO5 <- WHO5_plot(mental_wellbeing_data, "who5_21d", "I woke up feeling fresh and rested")
p5_WHO5 <- WHO5_plot(mental_wellbeing_data, "who5_21e", "My daily life has been filled with things that interest me")

# Print the WHO5 plots
print(p1_WHO5)
print(p2_WHO5)
print(p3_WHO5)
print(p4_WHO5)
print(p5_WHO5)

```

Now, we visualize the WHO5 result for all kids in our sample 

```{r}
WHO5_data <- mental_wellbeing_data   %>%
  rowwise() %>%
  mutate(WHO5_value = (who5_21a + who5_21b + who5_21c + who5_21d + who5_21e) * 4) %>%
  ungroup()

# Create a summary dataset with unique Kids_ID and their WHO5_value
WHO5_data <- WHO5_data %>%
  select(Kids_ID, WHO5_value) %>%
  distinct(Kids_ID, .keep_all = TRUE)

# Plot
ggplot(WHO5_data, aes(x = factor(Kids_ID), y = WHO5_value, fill = WHO5_value < 28)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  geom_hline(yintercept = 50, linetype = "dashed", color = "blue", size = 1) +
  geom_hline(yintercept = 28, linetype = "dashed", color = "red", size = 1) +
  scale_fill_manual(values = c("TRUE" = "red", "FALSE" = "steelblue")) +
  labs(title = "WHO5 Value by Kids_ID",
       x = "Kids ID",
       y = "WHO5 Value",
       caption = "Red bars indicate indicative of depression.") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

```
join WHO5 values into mental_wellbeing_data for further analysis
```{r}
mental_wellbeing_data <- mental_wellbeing_data %>%
  left_join(WHO5_data %>% select(Kids_ID, WHO5_value), by = "Kids_ID")
```

Please note that even though data preparation is done for WHO5, this indicator is not used in statistical testing of this study due to time limitations

----------------------------------------------------------------------------------------------------------------------

now we visualise GAD-7 data. This section involves variables gad_22a	gad_22b	gad_22c	gad_22d	gad_22e	gad_22f	gad_22g

```{r}


# Function to plot a bar plot for GAD-7 answers
GAD7_plot <- function(mental_wellbeing_data, column_name, title) {
  ggplot(mental_wellbeing_data, aes(x=factor(mental_wellbeing_data[[column_name]], labels=c("Not at all", "Several days", "Over half the days", "Nearly everyday")))) +
    geom_bar(fill="steelblue") +
    labs(title=title, x="Frequency", y="Count") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 46, hjust = 1))
}

# Plot bar plots for each variable
p1_GAD7 <- GAD7_plot(mental_wellbeing_data, "gad_22a", "Feeling nervous, anxious, or on edge")
p2_GAD7 <- GAD7_plot(mental_wellbeing_data, "gad_22b", "Not being able to stop or control worrying")
p3_GAD7 <- GAD7_plot(mental_wellbeing_data, "gad_22c", "Worrying too much about different things")
p4_GAD7 <- GAD7_plot(mental_wellbeing_data, "gad_22d", "Trouble relaxing")
p5_GAD7 <- GAD7_plot(mental_wellbeing_data, "gad_22e", "Being so restless that it's hard to sit still")
p6_GAD7 <- GAD7_plot(mental_wellbeing_data, "gad_22f", "Becoming easily annoyed or irritable")
p7_GAD7 <- GAD7_plot(mental_wellbeing_data, "gad_22g", "Feeling afraid as if something awful might happen")

# Print the plots
print(p1_GAD7)
print(p2_GAD7)
print(p3_GAD7)
print(p4_GAD7)
print(p5_GAD7)
print(p6_GAD7)
print(p7_GAD7)
```

create the plot for GAD-7 before adjusting the number of levels 
```{r}
GAD7_data <- mental_wellbeing_data %>%
  rowwise() %>%
  mutate(GAD7_value = sum(c(gad_22a, gad_22b, gad_22c, gad_22d, gad_22e, gad_22f, gad_22g), na.rm = TRUE)) %>%
  ungroup() %>%
  select(record_id, Kids_ID, GAD7_value) %>%
  distinct(Kids_ID, .keep_all = TRUE)

GAD7_data <- GAD7_data %>%
  mutate(anxiety_level = case_when(
    GAD7_value < 5 ~ "Below Mild",
    GAD7_value >= 5 & GAD7_value < 10 ~ "Mild",
    GAD7_value >= 10 & GAD7_value < 15 ~ "Moderate",
    GAD7_value >= 15 ~ "Severe"
  ))

GAD7_data <- GAD7_data %>%
  mutate(record_id = factor(record_id, levels = GAD7_data$record_id[order(-GAD7_value)]))

# Create a bar plot with unique colors for each anxiety level
GAD7_plot <- ggplot(GAD7_data, aes(x = factor(record_id), y = GAD7_value, fill = anxiety_level)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c(
    "Below Mild" = "lightblue",
    "Mild" = "yellow",
    "Moderate" = "orange",
    "Severe" = "red"
  )) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "blue", size = 1) +
  geom_hline(yintercept = 10, linetype = "dashed", color = "orange", size = 1) +
  geom_hline(yintercept = 15, linetype = "dashed", color = "red", size = 1) +
  labs(x = "Record ID",
       y = "GAD7 Score",
       fill = "Anxiety Level") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        panel.background = element_rect(fill = "white", colour = "white"), 
        plot.background = element_rect(fill = "white", colour = "white"))

ggsave(filename = "GAD7_scores_distribution.png", 
       plot = GAD7_plot,
       width = 8, height = 6, unit = "in", 
       dpi = 300)

GAD7_plot
```

get the min, max and mean for GAD-7 values
```{r}
anxiety_stats <- GAD7_data %>%
  summarise(
    min_GAD7 = min(GAD7_value),
    max_GAD7 = max(GAD7_value),
    mean_GAD7 = mean(GAD7_value)
  )

anxiety_stats
```

plot the number of observations under each level 
```{r}
anxiety_counts <- GAD7_data %>%
  count(anxiety_level) %>%
  mutate(Percentage = n / sum(n) * 100)

# Visualize the bar plot for each anxiety level showing number and percentage
anxiety_level_plot <- ggplot(anxiety_counts, aes(x = anxiety_level, y = n, fill = anxiety_level)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste(n, "(", sprintf("%.2f%%", Percentage), ")", sep = "")),
            position = position_dodge(width = 0.9), vjust = -0.25) +
  scale_fill_manual(values = c(
    "Below Mild" = "lightblue",
    "Mild" = "yellow",
    "Moderate" = "orange",
    "Severe" = "red"
  )) +
  labs(x = "Anxiety Level",
       y = "Number of Observations") +
  theme_minimal() +
  theme(panel.background = element_rect(fill = "white", colour = "white"), 
        plot.background = element_rect(fill = "white", colour = "white"),
        legend.position = "none")  

# Display the plot
print(anxiety_level_plot)

# Save the plot
ggsave(filename = "GAD7_anxiety_level_distribution.png", 
       plot = anxiety_level_plot,
       width = 8, height = 6, unit = "in", 
       dpi = 300)
```


Print kids who fall into Severe
```{r}
severe_anxiety_kids <- GAD7_data %>%
  filter(anxiety_level == "Severe")

print(severe_anxiety_kids)

```


We need to create a new factor called anxiety_level_bi, and use 8 as the cut-off point. The purpose of this operation is lowering the number of levels for Anxiety. After this operation, Anxiety will only have 2 levels. 
```{r}

GAD7_data <- GAD7_data %>%
  mutate(anxiety_level_bi = ifelse(GAD7_value >= 8, "Anxiety", "No Anxiety"))

GAD7_data
```

Join GAD7_data into mental_wellbeing_data
```{r}
mental_wellbeing_data <- mental_wellbeing_data %>%
  left_join(GAD7_data %>% select(Kids_ID, GAD7_value, anxiety_level, anxiety_level_bi), by = "Kids_ID")
```

create the plot for PHQ-9 before adjusting the number of levels 

```{r}

# Calculate PHQ-9 total score for each Kids_ID
PHQ9_data <- mental_wellbeing_data %>%
  rowwise() %>%
  mutate(PHQ9_value = sum(c(pleasure, depress, sleep, fatigue, satiety, negative, concentration, motion_speech, suicide_ideation), na.rm = TRUE)) %>%
  ungroup() %>%
  select(record_id, Kids_ID, PHQ9_value) %>%
  distinct(Kids_ID, .keep_all = TRUE)

# Categorize PHQ-9 total scores into depression severity levels
PHQ9_data <- PHQ9_data %>%
  mutate(depression_level = case_when(
    PHQ9_value <= 4 ~ "Minimal",
    PHQ9_value >= 5 & PHQ9_value <= 9 ~ "Mild",
    PHQ9_value >= 10 & PHQ9_value <= 14 ~ "Moderate",
    PHQ9_value >= 15 & PHQ9_value <= 19 ~ "Moderately severe",
    PHQ9_value >= 20 ~ "Severe"
  ))

PHQ9_data <- PHQ9_data %>%
  mutate(record_id = factor(record_id, levels = PHQ9_data$record_id[order(-PHQ9_value)]))

# Create a bar plot with unique colors for each depression level
PHQ9_plot <- ggplot(PHQ9_data, aes(x = factor(record_id), y = PHQ9_value, fill = depression_level)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c(
    "Minimal" = "lightgreen",
    "Mild" = "yellow",
    "Moderate" = "orange",
    "Moderately severe" = "darkorange",
    "Severe" = "red"
  )) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "blue", size = 1) +
  geom_hline(yintercept = 10, linetype = "dashed", color = "orange", size = 1) +
  geom_hline(yintercept = 15, linetype = "dashed", color = "darkorange", size = 1) +
  geom_hline(yintercept = 20, linetype = "dashed", color = "red", size = 1) +
  labs(x = "Record ID",
       y = "PHQ-9 Score",
       fill = "Depression Level") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        panel.background = element_rect(fill = "white", colour = "white"), 
        plot.background = element_rect(fill = "white", colour = "white"))

# Save the plot
ggsave(filename = "PHQ9_scores_distribution.png", 
       plot = PHQ9_plot,
       width = 8, height = 6, unit = "in", 
       dpi = 300)


```

Now, we print the most conerning kids
```{r}

severe_depression_kids <- PHQ9_data %>%
  filter(depression_level == "Severe")

print(severe_depression_kids)

```

now, we calculate the min, max and mean for PHQ-9 data
```{r}
PHQ9_stats <- PHQ9_data %>%
  summarise(
    min_PHQ9 = min(PHQ9_value),
    max_PHQ9 = max(PHQ9_value),
    mean_PHQ9 = mean(PHQ9_value)
  )
PHQ9_stats
```

we can also visualise the number of observations under each level. apparently, some levels have two few observations. therefore, we need to reduce the number of levels for Depression 
```{r}
PHQ9_data$depression_level <- factor(PHQ9_data$depression_level, 
                                     levels = c("Minimal", "Mild", "Moderate", "Moderately severe", "Severe"))

# Count the number of observations for each depression level and calculate the percentage
depression_counts <- PHQ9_data %>%
  count(depression_level) %>%
  mutate(Percentage = n / sum(n) * 100)

# Visualize the bar plot for each depression level showing number and percentage
depression_level_plot <- ggplot(depression_counts, aes(x = depression_level, y = n, fill = depression_level)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste(n, "(", sprintf("%.2f%%", Percentage), ")", sep = "")),
            position = position_dodge(width = 0.9), vjust = -0.25) +
  scale_fill_manual(values = c(
    "Minimal" = "lightgreen",
    "Mild" = "yellow",
    "Moderate" = "orange",
    "Moderately severe" = "darkorange",
    "Severe" = "red"
  )) +
  labs(x = "Depression Level",
       y = "Number of Observations") +
  theme_minimal() +
  theme(panel.background = element_rect(fill = "white", colour = "white"), 
        plot.background = element_rect(fill = "white", colour = "white"),
        legend.position = "none")  

# Display the plot
print(depression_level_plot)

# Save the plot
ggsave(filename = "PHQ9_depression_level_distribution.png", 
       plot = depression_level_plot,
       width = 8, height = 6, unit = "in", 
       dpi = 300)
```


Just like GAD-7, PHQ-9 levels also need to be restructured, with the cut-point of 10
```{r}
PHQ9_data <- PHQ9_data %>%
  mutate(depression_level_bi = ifelse(PHQ9_value >= 10, "Depression", "No Depression"))

PHQ9_data
```


To visualise for PHQ-9 after adjusting the number of levels 

```{r}
# Create a bar plot with unique colors for each depression_level_bi
PHQ9_plot_bi <- ggplot(PHQ9_data, aes(x = factor(record_id), y = PHQ9_value, fill = depression_level_bi)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c(
    "Depression" = "red",
    "No Depression" = "lightblue"
  )) +
  geom_hline(yintercept = 10, linetype = "dashed", color = "black", size = 1) +
  labs(x = "Record ID",
       y = "PHQ9 Score",
       fill = "Depression Level Binary") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
        panel.background = element_rect(fill = "white", colour = "white"), 
        plot.background = element_rect(fill = "white", colour = "white"))

# Save the plot
ggsave(filename = "PHQ9_scores_binary_distribution.png", 
       plot = PHQ9_plot_bi,
       width = 8, height = 6, unit = "in", 
       dpi = 300)

# Display the plot
PHQ9_plot_bi

```


```{r}
# Join PHQ9_data into mental_wellbeing_data based on Kids_ID
mental_wellbeing_data <- mental_wellbeing_data %>%
  left_join(PHQ9_data %>% select(Kids_ID, PHQ9_value, depression_level, depression_level_bi), by = "Kids_ID")
```

----------------------------------------------------------------------------------------------------------------------

Now, we explore the distribution of each answer for ASQ data. Since ASQ does not have clear cut-off points, this study does not investigate further. 

```{r}
# Function to plot a histogram for a given ASQ column in the dataframe
ASQ_plot <- function(mental_wellbeing_data, column_name, title, labels) {
  ggplot(mental_wellbeing_data, aes(x=factor(mental_wellbeing_data[[column_name]], levels = 1:5, labels = labels))) +
    geom_bar(fill="steelblue") +
    labs(title=title, x="", y="Count") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 46, hjust = 1))
}

# Labels for the asq_a_29_* variables (A)
labels_a <- c("Almost all of the time", "A lot of the time", "Some of the time", "A little of the time", "Hardly ever")

# Labels for the asq_b_30_* variables (B)
labels_b <- c("Strongly agree", "Agree", "Neither agree nor disagree", "Disagree", "Strongly disagree")

# Plot histograms for each ASQ variable
p1_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_a_29_a", "1. I am able to stand up for myself and what I believe in", labels_a)
p2_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_a_29_b", "2. How I feel about myself depends on what others think of me", labels_a)
p3_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_a_29_c", "3. I feel I can be myself around other people", labels_a)
p4_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_a_29_d", "4. I make an effort to look good", labels_a)
p5_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_a_29_e", "5. Overall I feel good about my abilities compared to others", labels_a)
p6_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_a_29_f", "6. If I make an innocent mistake I let it get me down", labels_a)
p7_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_a_29_g", "7. I feel useless", labels_a)
p8_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_b_30_a", "8. Overall I like who I am", labels_b)
p9_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_b_30_b", "9. I am a good person who has a lot to offer", labels_b)
p10_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_b_30_c", "10. I feel that I am a valuable person who is at least equal to other people", labels_b)
p11_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_b_30_d", "11. How I feel about my body makes me feel less confident", labels_b)
p12_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_b_30_e", "12. I feel confident in my abilities to achieve the things I set my mind to", labels_b)
p13_ASQ <- ASQ_plot(mental_wellbeing_data, "asq_b_30_f", "13. I think other people like me", labels_b)

# Print the ASQ plots
print(p1_ASQ)
print(p2_ASQ)
print(p3_ASQ)
print(p4_ASQ)
print(p5_ASQ)
print(p6_ASQ)
print(p7_ASQ)
print(p8_ASQ)
print(p9_ASQ)
print(p10_ASQ)
print(p11_ASQ)
print(p12_ASQ)
print(p13_ASQ)


```

----------------------------------------------------------------------------------------------------------------------

Now, we can merge all the existing data summurised from Well-being EDA, demo_EDA and Sleep_data_wrangling
```{r}
mental_wellbeing_summary <- select(mental_wellbeing_data, 
                                   Kids_ID, 
                                   WHO5_value, 
                                   GAD7_value, 
                                   anxiety_level, 
                                   anxiety_level_bi,
                                   PHQ9_value, 
                                   depression_level,
                                   depression_level_bi)
wellbeing_demo2024 <- merge(mental_wellbeing_summary, demo_data2024, by = "Kids_ID")
wellbeing_demo_sleep2024 <- merge(sleep_hours_schoolday, wellbeing_demo2024, by = "Kids_ID") 
wellbeing_demo_sleep2024
```


We can perform some further analysis without incorporating app-specific data. Here we can perform pair-wise Chi-squared test on "Underslept", "Gender", "Ethnic.group", "Decile_group", "anxiety_level_bi " and "depression_level_bi" to see if there is any significant association

we can find 5 pairs show significant association: 

```{r}
variables <- c("Underslept", "Gender", "Ethnic.group", "Decile_group", "anxiety_level_bi", "depression_level_bi")

# Initialize a matrix to store p-values
p_value_matrix <- matrix(nrow = length(variables), ncol = length(variables), 
                         dimnames = list(variables, variables))

# create a loop to calculate p-values for each pair of variables
for (i in 1:length(variables)) {
  for (j in 1:length(variables)) {
    if (i != j) {
      # Ensure both variables are factors for Chi-squared test
      var1 <- factor(wellbeing_demo_sleep2024[[variables[i]]])
      var2 <- factor(wellbeing_demo_sleep2024[[variables[j]]])
      # Perform Chi-squared test
      test_result <- tryCatch({
        chisq.test(var1, var2)
      }, error = function(e) {
        # Return NA for p-value if the test fails
        return(list(p.value = NA))
      })
      # Store the p-value in the matrix
      p_value_matrix[i, j] <- test_result$p.value
    } else {
      # finally, we exclude scenarios where a variable is compared to itself
      p_value_matrix[i, j] <- NA
    }
  }
}

# Output the result
print(p_value_matrix)
```

print the pairs of catagorical with significant correlation
```{r}

for (i in 1:(nrow(p_value_matrix) - 1)) 
  for (j in (i + 1):ncol(p_value_matrix)) 
    if (p_value_matrix[i, j] < 0.05) 
      # Print only the variable pairs that have a significant association
      cat(variables[i], "and", variables[j], "\n")

```
